\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-03-21 paper/main.tex
saving space

@@

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}
%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation email}{June 03--05,
  2018}{Woodstock, NY}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}
\acmISBN{978-1-4503-XXXX-X/2018/06}
\acmBooktitle{Companion Proceedings of the 33rd ACM Symposium on the Foundations
of Software Engineering (FSE '25), June 23--27, 2025, Trondheim, Norway}

@@

The following video demonstrates some
of the features of \tname:

>>>>

\setcopyright{none} % to remove the copyright notice
\settopmatter{printacmref=false} % to remove the ACM Reference Format
\renewcommand\footnotetextcopyrightpermission[1]{} % to remove copyright box

@@

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
%% \setcopyright{acmlicensed}
%% \copyrightyear{2018}
%% \acmYear{2018}
%% \acmDOI{XXXXXXX.XXXXXXX}
%% %% These commands are for a PROCEEDINGS abstract or paper.
%% \acmConference[Conference acronym 'XX]{Make sure to enter the correct
%%   conference title from your rights confirmation email}{June 03--05,
%%   2018}{Woodstock, NY}
%% %%
%% %%  Uncomment \acmBooktitle if the title of the proceedings is different
%% %%  from ``Proceedings of ...''!
%% %%
%% %%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%% %%  June 03--05, 2018, Woodstock, NY}
%% \acmISBN{978-1-4503-XXXX-X/2018/06}
%% \acmBooktitle{Companion Proceedings of the 33rd ACM Symposium on the Foundations
%% of Software Engineering (FSE '25), June 23--27, 2025, Trondheim, Norway}

@@

The following video demonstrates \tname:
